Software Citation Principles

### 2016-03-31 sc-principles/software-citation-principles.tex
adding other WSSSPE report cites

While not usually expressed as software citation principles, a number of groups have developed community guidelines around software and data citation. Van de Sompel et al.~\cite{VandeSompel2004} argue for registration of all units of scholarly communication, including software. In a `Publish or be damned? An alternative impact manifesto for research software'~\cite{ssi-publish-or-be-damned}, Chue Hong lists nine principles as part of `The Research Software Impact Manifesto'.

@@

Most notable of the community efforts are those of WSSSPE~\cite{wssspe} and
SSI~\cite{ssi-workshops}, who between them have run a series of workshops aimed
at gathering together community members with an interest in 1) defining the set of problems
related to the role of software and associated people in research settings, particularly academia,
2) discussing potential solutions to those problems, and 3) beginning to work on implementing
some of those solutions.
%\asnote{Not sure this is a sufficient one-line
%summary but couldn't think of anything better.} \katznote{I've edited it a bit}
In each of the three years that
WSSSPE workshops have run thus far, the participants have produced a report
documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3}
has some preliminary work and discussion particularly relevant to this working
group.
Up
In addition, a number of academic publishers such as APA~\cite{APA-guidelines} have recommendations for submitting authors on how to cite software and journals such as F1000Research~\cite{F1000}, SoftwareX~\cite{softwareX}, and Open Research Computation~\cite{softwareX} allow for submissions entirely focussed on research software.

>>>>

While not usually expressed as software citation principles, a number of groups have developed community guidelines around software and data citation. Van de Sompel et al.~\cite{VandeSompel2004} argue for registration of all units of scholarly communication, including software. In ``Publish or be damned? An alternative impact manifesto for research software''~\cite{ssi-publish-or-be-damned}, Chue Hong lists nine principles as part of `The Research Software Impact Manifesto'.

@@

Most notable of the community efforts are those of WSSSPE~\cite{wssspe} and
SSI~\cite{ssi-workshops}, who between them have run a series of workshops aimed
at gathering together community members with an interest in 1) defining the set of problems
related to the role of software and associated people in research settings, particularly academia,
2) discussing potential solutions to those problems, and 3) beginning to work on implementing
some of those solutions.
%\asnote{Not sure this is a sufficient one-line
%summary but couldn't think of anything better.} \katznote{I've edited it a bit}
In each of the three years that
WSSSPE workshops have run thus far, the participants have produced a report~\cite{WSSSPE1,WSSSPE2,WSSSPE3}
documenting the topics covered. Section 5.8 and Appendix J in the WSSSPE3 report~\cite{WSSSPE3}
has some preliminary work and discussion particularly relevant to this working
group.
Up
In addition, a number of academic publishers such as APA~\cite{APA-guidelines} have recommendations for submitting authors on how to cite software and journals such as F1000Research~\cite{F1000}, SoftwareX~\cite{softwareX}, and Open Research Computation~\cite{softwareX} allow for submissions entirely focussed on research software.
